\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-12-15 Response.tex

\textit{A new geometric adaptive control scheme for the stabilization of the attitude dynamics of a rigid body with state inequality constraints is studied in this paper and ensures that the closed-loop system is asymptotically stable in the sense of Lyapunov stability. The main contribution and result are well presented and organized. Therefore, it is sufficient to be accepted in this journal provided that the following minor problems are considered in the revised version.
}

% \setlength{\leftmargini}{0pt}
\begin{enumerate}

\item \textit{ In general, the external disturbance is a time-varying signal even though it is bounded. Thus, authors should consider the time-varying disturbance case.}

It is true that typically, the external disturbances on a system will be time varying.
However, the form of uncertainty shown in \( (1) \) is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}.
As a result, we use this same form of uncertainty, namely that the uncertain disturbance is additive in nature and enters through the input channel.
In addition, a wide variety of disturbances in the aerospace engineering field are accurately represented by this formulation and several examples are given in the article.
Furthermore, it has been shown in~\cite{ioannou2012} that this form of adaptive control is able to handle time-varying uncertainties in which the uncertain term is varying sufficiently slowly as compared to the controlled dynamics. 
We have improved the manuscript with an additional numerical experiment in~\Cref{ssec:time_varying} demonstrating the ability of the adaptive controller to handle time-varying disturbances.
The additional content is duplicated here:
\begin{correction}
    The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}. 
    A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters, are accurately represented via this model. 
    In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
    For example, Euler's law gives the relationship for the rate of change of angular momentum
    \begin{align*}
        M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
    \end{align*}
    Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
    Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.

### 2016-12-15 Response.tex

\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in,centering]{geometry}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amssymb}  
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{siunitx}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{color}
\usepackage{bm}
\usepackage{xr-hyper}
\usepackage{hyperref}
\usepackage[]{cleveref} % get fancy referencing

\externaldocument[]{manuscript}[manuscript.pdf]

@@

In this work, we are focused on the design of attitude controllers in the presence of state inequality constraints. 
The addition of an adaptive update law allows the system to stabilize in the presence of unknown external disturbances.
We are not considering the case of an unknown inertia matrix, but rather assume that there exists accurate knowledge of the rigid body. 
This assumption is relatively simple to satisfy as any physical control system will first have an accurate model of the system itself.
For example, the mass and inertia properties of all spacecraft are accurately measured and verified prior to launch.

In addition, the uncertainty model presented in the paper is commonly used in the adaptive control literature.
Also, it is possible to represent a uncertain or varying inertia matrix as an external disturbance torque. 
Additional detail has been added to the manuscript in~\Cref{ssec:time_varying} and is duplicated in the previous answer.

\item \textit{The state inequality constraint is not violated based on adding the repulsive term in the attitude error function. Is this result still valid if this constraint becomes time-dependent?}

In this work, we are specifically concerned with presenting a geometric attitude controller on \( \SO \) in the presence of state inequality constraints.
More specifically, we are assuming that these constraints are time-invariant rather than time dependent. 
This type of constraint is representative of the attitude constraints that are frequently experienced in the attitude control of spacecraft. 
For example, various keep-out zones for sensitive electro-optical sensors are well represented as a fixed constraint in the inertial frame. 
Also, as discussed above, the revised manuscript includes additional numerical results illustrating that the proposed approach can handle time-varying uncertainties while satisfying the inequality constraints.

Furthermore, the time scale of the attitude dynamics, and therefore any attitude control manuever, is much shorter than the time scale of the translational dynamics.
In other words, a time-dependent constraint in the inertial frame will evolve at a much slower rate as compared to the attitude dynamics. 
As a result, it is possible to model the time-varying constraints as a series of time-invariant constraints in the inertial frame. 
In this situation, the presented approach allows for a straightforward method to design an attitude stabilization control law. 
However, this is a very good suggestion and it is an area of current research effort.

### 2016-12-15 Response.tex

\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\newcommand{\RI}{\text{\RNum{1}}}
\newcommand{\RII}{\text{\RNum{2}}}
\newcommand{\RIII}{\text{\RNum{3}}}

\newtheorem{definition}{Definition}
\newtheorem{lem}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{cor}{Corollary}

@@

\end{enumerate}

\subsection*{Reviewer 3}

\textit{This paper considers the attitude control with inequality constraints. Attitude dynamics with matched uncertainty which is parameterized by a unknown constant matrix, and hard constants expressed by rotation matrix are considered. Although the problem is very interesting, the proofs for major results on the case with plant uncertainty are far from complete. Some comments are listed below.}

\begin{enumerate}
\item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}

The variation of the rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}
We have augmented the proof of Proposition 1, which is given in Appendix 1, to include the definition of the variation as:
\begin{correction}
The infinitesimal variation of a rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}

\end{correction}

In addition,~\Cref{prop:config_error} was modified to include additional detail on the notation \( \dirDiff{f}{x}\) as
\begin{correction}
    The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
    \begin{align*}
        \dirDiff{B}{R} &= \eta \cdot e_{R_{B}} ,
    \end{align*}
  where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
\end{correction}
\item \textit{This is serious. In section 2, the upper bounds listed in Proposition 4 are given. Well, these should be the properties that your controller guarantees not come from the set D you've defined. Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}

@@

\item \textit{Typo in eq. (40).}

The equation has been modified as:
\begin{correction}
\begin{gather}
    0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H} ,
\end{gather}
\end{correction}

\item \textit{Abuse of notation 'hat' and 'vee' in equations (6)-(8)}

The \( \wedge : \R^3 \to \so \) and \( \vee : \so \to \R^3 \) operators are used according to the convention that is common in the literature~\cite{lee2010,lee2011a}.
In this case, the \textit{hat} operator is equivalently represented as \( \hat{x} = \parenth{x}^\wedge \).
This representation enables a consistent notation for both short/simple terms, such as \( \hat{x} \) and more complicated terms such as \(\parenth{R^T v}^\wedge\). 
Finally, this dual usage of the notation drastically improves the quality of the resulting typography.

Explicit detail has been added to the manuscript to explain this dual notation of the \textit{hat} and \textit{vee} maps.
\begin{correction}
We use the notation \( \hat{x}, x\) and \( \parenth{x}^\wedge\) interchangeably.
In particular, we use the latter form when the expression for the argument of the \textit{hat} map is long. 
\end{correction}
\end{enumerate}
